Modelling last glacial cycle ice dynamics in the Alps

### 2017-09-18 articles/cycle/alps-cycle.tex
Add references on trimlines.

>>>>

    Following the general assumption that trimlines, which mark the transition
    between the steep frost-shattered ridges and the more gentle glacially eroded
    valley troughs, represent the maximum elevation of the LGM ice surface,
    the LGM ice thickness in the Alps been reconstructed in several areas
    \citep{Husen.1987, Florineth.1998, Florineth.Schluchter.1998,
    Kelly.etal.2004, Bini.etal.2009, Coutterand.2010, Cossart.etal.2012}.
    However, this assumption is challenged by geological evidence from
    Scandinavia \citep[e.g.,]{Kleman.1994, Kleman.Borgstrom.1994,
    Stroeven.etal.2002}, the British Isles \citep[e.g.,]{Fabel.etal.2012}, and
    North America \citep[e.g.,]{Kleman.etal.2010}, that pre-glacial landscapes
    located well above the trimlines have been glaciated and preserved under
    under cold-based ice, sometimes for several glacial cycles.
